Statistical Inference for inter-arrival times of extreme events in bursty time series

### 2018-12-05 article_springer/article_springer.Rmd
Some graphical changes

```{r thresholdedBursty, message=FALSE, fig.height=4, fig.width=6, fig.cap="\\label{fig:thresholdedBursty}Exceedances (red) and Times until Exceedance (durations between blue crosses) for a given threshold $\\ell$ (dashed line)."}
tail <- params$tail
n <- params$n 
sigma <- (cos(pi*tail/2))^(1/tail)

times <- cumsum(stabledist::rstable(n, tail, 1, sigma, pm=1))
#times<-cumsum(rpareto(n,tail))
magnitudes <- extRemes::revd(n, scale = 1, shape = 0)
sim_ctre <- ctre(data.frame(times, magnitudes)) 
par(mfrow = c(2,1)) 
p1 <- plot(sim_ctre, p = 0.01, main = "Simulated MRP") 
p2 <- flares %>% ctre() %>% plot(p = 0.02, log = 'y', main = "HXRBS data") 
library(gridExtra)
grid.arrange(p1, p2, nrow = 2)
```

@@

```{r Hillplots, echo=FALSE, fig.height=12, fig.cap="\\label{fig:Hillplots} Hillplots for simulated Mittag-Leffler distributed rv's with tail parameter 0.5 (two plots in the right column) and 0.8 (two plots in the left column) and sample sizes 200 (two plots in the lower row) and 1000 (two plots in the upper row). ", out.width = '100%'}
# knitr::include_graphics("Hillplots.pdf")
```

@@

```{r LRT power, echo=FALSE, fig.cap="\\label{Fig:LRT} Power for bootstrapped LRT for different sample sizes", out.width = '100%'}
knitr::include_graphics("Plots_LRT_boot.pdf")
```

@@

```{r simulated-example, message=FALSE, warning=FALSE, fig.cap=caption}
k_max <- 500

thin_sim_ctre <- thin(ctre = sim_ctre, k = k_max)
# par(mfrow=c(1,2))
MLestimates(ctre = thin_sim_ctre, tail = params$tail, scale = n^(1/params$tail))
```

@@

```{r Ex1figsScale, echo=FALSE,fig.height=7,fig.cap="\\label{Fig:Ex1figsScale} Stability Plots for the scale parameter for Example 1 (stable distributed waiting times, true scale parameter = 1).", fig.show='hold', out.width = '45%'}
knitr::include_graphics(c("SimuStudy_StabilityPlots_Ex1_Scales_logMoms.pdf","SimuStudy_StabilityPlots_Ex1_Scales_mles.pdf"))
```

```{r Ex2figsScale, echo=FALSE,fig.height=7,fig.cap="\\label{Fig:Ex2figsScale} Stability Plots for the scale parameter m=100 simulation runs for Example 2 (stable distributed waiting times, true scale parameter = 1).", fig.show='hold', out.width = '45%'}
knitr::include_graphics(c("SimuStudy_StabilityPlots_Ex2_Scales_logMoms.pdf","SimuStudy_StabilityPlots_Ex2_Scales_mles.pdf"))
```

```{r Ex3figsScale, echo=FALSE,fig.height=7,fig.cap="\\label{Fig:Ex3figsScale} Stability Plots for the scale parameter for m=100 simulation runs for Example 3 (stable distributed waiting times, true scale parameter = 1).", fig.show='hold', out.width = '45%'}
knitr::include_graphics(c("SimuStudy_StabilityPlots_Ex3_Scales_logMoms.pdf","SimuStudy_StabilityPlots_Ex3_Scales_mles.pdf"))
```
\newpage

>>>>

```{r thresholdedBursty, message=FALSE, fig.height=3, fig.width=8, fig.cap="\\label{fig:thresholdedBursty}Exceedances (red) and Times until Exceedance (durations between blue crosses) for a given threshold $\\ell$ (dashed line)."}
tail <- params$tail
n <- params$n 
sigma <- (cos(pi*tail/2))^(1/tail)

times <- cumsum(stabledist::rstable(n, tail, 1, sigma, pm=1))
#times<-cumsum(rpareto(n,tail))
magnitudes <- extRemes::revd(n, scale = 1, shape = 0)
sim_ctre <- ctre(data.frame(times, magnitudes)) 
par(mfrow = c(1,2)) 
p1<-plot(sim_ctre, p = 0.01, main = "Simulated MRP") 
p2<-flares %>% ctre() %>% plot(p = 0.02, log = 'y', main = "HXRBS data") 
```

@@

```{r Hillplots, echo=FALSE, fig.align="center", fig.cap="\\label{fig:Hillplots} Hillplots for simulated Mittag-Leffler distributed rv's with tail parameter 0.5 (two plots in the right column) and 0.8 (two plots in the left column) and sample sizes 200 (two plots in the lower row) and 1000 (two plots in the upper row). ", out.width = '90%'}
 knitr::include_graphics("Hillplots.pdf")
```

@@

```{r LRT power, echo=FALSE, fig.align="center", fig.cap="\\label{Fig:LRT} Power for bootstrapped LRT for different sample sizes", out.width = '80%'}
knitr::include_graphics("Plots_LRT_boot.pdf")
```

@@

<!-- ```{r simulated-example, message=FALSE, warning=FALSE, fig.cap=caption} -->
<!-- k_max <- 500 -->

<!-- thin_sim_ctre <- thin(ctre = sim_ctre, k = k_max) -->
<!-- # par(mfrow=c(1,2)) -->
<!-- MLestimates(ctre = thin_sim_ctre, tail = params$tail, scale = n^(1/params$tail)) -->
<!-- ``` -->

@@

```{r Ex1figsScale, echo=FALSE,fig.height=7,fig.cap="\\label{Fig:Ex1figsScale} Stability Plots for the scale parameter for Example 1 (stable distributed waiting times, true scale parameter = 1).", fig.show='hold', out.width = '40%'}
knitr::include_graphics(c("SimuStudy_StabilityPlots_Ex1_Scales_logMoms.pdf","SimuStudy_StabilityPlots_Ex1_Scales_mles.pdf"))
```

```{r Ex2figsScale, echo=FALSE,fig.height=7,fig.cap="\\label{Fig:Ex2figsScale} Stability Plots for the scale parameter m=100 simulation runs for Example 2 (stable distributed waiting times, true scale parameter = 1).", fig.show='hold', out.width = '40%'}
knitr::include_graphics(c("SimuStudy_StabilityPlots_Ex2_Scales_logMoms.pdf","SimuStudy_StabilityPlots_Ex2_Scales_mles.pdf"))
```

```{r Ex3figsScale, echo=FALSE,fig.height=7,fig.cap="\\label{Fig:Ex3figsScale} Stability Plots for the scale parameter for m=100 simulation runs for Example 3 (stable distributed waiting times, true scale parameter = 1).", fig.show='hold', out.width = '40%'}
knitr::include_graphics(c("SimuStudy_StabilityPlots_Ex3_Scales_logMoms.pdf","SimuStudy_StabilityPlots_Ex3_Scales_mles.pdf"))
```
\newpage
